Contribution Title\thanks{Supported by organization x.}

### 2019-12-17 sections/evaluation.tex
update clause size reduction representation and description

Fig.~\ref{fig:t1} shows that $\IUIPPURE$ ($\IUIPPURE$) solved seven (five) more instances than the baseline solver with lower PAR-2 scores. $\IUIPPURE$ has marginally lower PAR-2 score than $\IUIPPURE$. Both $\IUIPPURE$ and $\IUIPMIN$ produce clause with significantly smaller size than 1-UIP by  20.4\% and 27.7\%, respectively. Fig.~\ref{fig:len_pdf} shows the probability density distribution (PDF) of the relative clause size of both i-uip learning schemes ($\IUIPPURE$ in red and $\IUIPMIN$ in green) for each instance. $\IUIPPURE$ ($\IUIPMIN$) produces shorter clauses for 76.5\% (88.25\%) of instances, and average relative reduction from 1-UIP is 16.7\% (18.6\%). Fig.~\ref{fig:len_compare} compares the absolute clause size of $\IUIPMIN$, $\IUIPPURE$ and 1-UIP, and it shows that both i-UIP learning schemes in general produce the smaller clauses, and the size reduction is more significant for instances with large average 1-UIP clause size. Moreover, $\IUIPMIN$ clauses (indicated in green) is consistently smaller than $\IUIPPURE$ clauses.

\begin{figure}
    \centering
    \includegraphics[width=0.8\textwidth,natwidth=610,natheight=642]{figures/factor_clause_length_PDF.png}
    \caption{ Relative Clause size distribution. X axis indicates the relative size of i-uip clause (with respect to 1-uip clause) for each instance, and Y axis indicates the probability density. $\IUIPMIN$ and $\IUIPPURE$ are illustrated with green and red, respectively}
     \label{fig:len_pdf}
\end{figure}
\begin{figure} \label{fig:len_compare}
    \centering
    \includegraphics[width=0.8\textwidth,natwidth=610,natheight=642]{i-uip-sizes-compare.png}
    \caption{Average clause size comparison plot. Each point in the plot represents an instance. X and Y axis shows the clause length from $\IUIP$ and 1-UIP, respectively. Each green (red) dot represents an compared instance between $\MapleBase$ and $\MapleIUIMIN$ ($\IUIPPURE$). }
    \label{fig:len_compare}
\end{figure}
\nf{ Do we need this?
We additionally looked at the 14 instances solved by $\IUIPMIN$ but not by 1-UIP. $\IUIPMIN$ produces smaller clauses for all of them with average relative reduction of 22\% and maximum 77\% (30 vs 135). Seven out of 14 instances has size relative reduction over 30\%. For the 9 instances solved by 1-UIP but not by $\IUIPMIN$, $\IUIPMIN$ only produce smaller clause for three instances and with average relative reduction of 3.3\%.}

>>>>

Fig.~\ref{fig:t1} shows that $\IUIPPURE$ ($\IUIPPURE$) solved seven (five) more instances than the baseline solver with lower PAR-2 scores. $\IUIPPURE$ has marginally lower PAR-2 score than $\IUIPPURE$. Both $\IUIPPURE$ and $\IUIPMIN$ produce clause with significantly smaller size than 1-UIP by  20.4\% and 27.7\%, respectively. Fig.~\ref{fig:len_pdf} shows the probability density distribution (PDF) of the relative clause size of both i-uip learning schemes ($\IUIPPURE$ in red and $\IUIPMIN$ in green) for each instance. $\IUIPPURE$ ($\IUIPMIN$) produces shorter clauses for 77.7\% (88.5\%) of instances, and average relative reduction from 1-UIP is 16.7\% (18.6\%). Fig.~\ref{fig:len_compare} compares the absolute clause size of $\IUIPMIN$, $\IUIPPURE$ and 1-UIP, and it shows that both i-UIP learning schemes in general produce the smaller clauses, and the size reduction is more significant for instances with large average 1-UIP clause size. Moreover, $\IUIPMIN$ clauses (indicated in green) is consistently smaller than $\IUIPPURE$ clauses.

\begin{figure}
    \centering
    \includegraphics[width=0.8\textwidth,natwidth=610,natheight=642]{figures/clause_reduction_PDF.png}
     \caption{ Relative clause size reduction distribution. X axis indicates the relative size of difference between i-uip and 1-uip clauses (calculated as $\dfrac{|\oneUIPClause|-|\iUIPClause|}{|\oneUIPClause|}$ ) for each instance, and Y axis shows the probability density.}
     \label{fig:len_pdf}
\end{figure}
\begin{figure} \label{fig:len_compare}
    \centering
    \includegraphics[width=0.8\textwidth,natwidth=610,natheight=642]{i-uip-sizes-compare.png}
    \caption{Average clause size comparison plot. Each point in the plot represents an instance. X and Y axis shows the clause length from $\IUIP$ and 1-UIP, respectively. Each green (red) dot represents an compared instance between $\MapleBase$ and $\MapleIUIMIN$ ($\IUIPPURE$). }
    \label{fig:len_compare}
\end{figure}
\nf{ Do we need this?
We additionally looked at the 14 instances solved by $\IUIPMIN$ but not by 1-UIP. $\IUIPMIN$ produces smaller clauses for all of them with average relative reduction of 22\% and maximum 77\% (30 vs 135). Seven out of 14 instances has size relative reduction over 30\%. For the 9 instances solved by 1-UIP but not by $\IUIPMIN$, $\IUIPMIN$ only produce smaller clause for three instances and with average relative reduction of 3.3\%.}
